Inference of proto-neutron star properties from gravitational-wave data in core-collapse supernovae.

### 2020-11-07 results.tex
A bit more work.

@@

@@

Table \ref{tab:results} reports the source distances $d_r$ in kpc at which the median of the coverage is lower than 95\% of the noise only values for aLIGO, AdV, and different configurations of third-generation detectors. We have checked that using either the median of the coverage or the median of $\Delta$ provide similar results for the distance.
These numbers are an estimate of the order of magnitude of the source maximal distance at which a
reconstruction of the ratio could be possible with current GW detectors.
They are also upper limits as we are taking into account the detector antenna response in our
simulation but consider the source is optimally oriented. 
Table \ref{tab:results} reports also $d_r$ for the Advanced Virgo detector at design sensitivity.
Results are very similar to aLIGO, despite the detector sensitivity differences.
Note that Table \ref{tab:results} provides the distance at which one could detect a source
optimally oriented with a matched filter signal-to-noise ratio of 13.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{plots/aLIGO_delta_allwvfs}
 \caption{Same as Fig.~\ref{fig:aLIGO_cov_allwvf} but for the relative error $\Delta$. \tf{Same comments as for Fig.~\ref{fig:aLIGO_cov_allwvf}.}}
% Median of $\Delta$ for 8 CCSN waveforms embedded in aLIGO noise and located at different distance from the Earth. The ``no signal'' line and band show the median and first and third quartile of $\Delta$ in absence of any signal.} 
\label{fig:aLIGO_prec_allwvf}
\end{figure}

The same analysis has been performed using expected sensitivity curves for the third generation of
GW detectors. In Europe the Einstein Telescope project proposes to host in a 10-km
equilateral triangle configuration 3 low-power low-frequency cryogenic interferometers as well as 3
high-power high-frequency interferometers. Three sensitivity curves, ET-B, ET-C and ET-D corresponding
to different options and stages of the project~\cite{Hild_2011} are considered in this study.
The US based project Cosmic Explorer~\cite{reitze2019cosmic} is proposing to reach its design
sensitivity circa 2040 through two phases labeled CE1 and CE2 also shown in Figure~\ref{fig:spectrum}.

Figure \ref{fig:s20--SFHo_all3G} shows $\Delta$ as function of the source distance for {\texttt s20S}
waveform for the five 3G detector configurations. Overall, the ratio is well reconstructed up to distances
in the range \unit[100--200]{kpc} which represents an improvement of a factor 10 with respect to
Advanced LIGO and Advanced Virgo detectors. We can also note that the Einstein Telescope results lay in
between the 2 Cosmic Explorer results. This is confirmed for all other waveforms, expect {\texttt s25}
for which the maximal distance reach in CE2 is significantly lower than CE1. This is partly due to the
small variation of the reconstruction quality to the distance of the source making the estimation of $d_r$
rather uncertain for this waveform. All results are summarized in Table \ref{tab:results} and Figure
\ref{fig:distances}. It is remarkable that with 3G detectors the ratio could be reconstructed for sources
located up to several hundred of kpc. It is nevertheless important to note the rather wide range obtained
for the different waveforms probing a large range of progenitor masses.
We did not find any correlation between the mass of the progenitor and $d_r$, nor the equation of state.
On the other hand, the quality
of the ratio reconstruction depends on the signal-to-noise ratio, expressed in Table \ref{tab:results} by
$d_{det}$.

>>>>

\tf{We probably need a better title for this section.}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.5\textwidth]{plots/aLIGO_delta_allwvfs}
 \caption{Same as Fig.~\ref{fig:aLIGO_cov_allwvf} but for the relative error $\Delta$. \tf{Same comments as for Fig.~\ref{fig:aLIGO_cov_allwvf}.}}
% Median of $\Delta$ for 8 CCSN waveforms embedded in aLIGO noise and located at different distance from the Earth. The ``no signal'' line and band show the median and first and third quartile of $\Delta$ in absence of any signal.} 
\label{fig:aLIGO_prec_allwvf}
\end{figure}

@@

We perform the same analysis using the design sensitivity curve of AdV and expected sensitivity curves for the third-generation 
GW detectors. The results for the former are reported in Table \ref{tab:results}. We focus now on third-generation detectors whose results are reported in Table \ref{tab:results} and shown in Fig.~\ref{fig:s20--SFHo_all3G}. In Europe the Einstein Telescope project proposes to host in a 10-km equilateral triangle configuration three low-power low-frequency cryogenic interferometers as well as three high-power high-frequency interferometers. Three sensitivity curves, ET-B, ET-C and ET-D corresponding to different options and stages of the project~\cite{Hild_2011} are considered in our study (cf.~Fig.~\ref{fig:spectrum}). The US based project Cosmic Explorer~\cite{reitze2019cosmic} is expecting to reach its design
sensitivity circa 2040 through two phases labeled CE1 and CE2, whose sensitivity curves are also shown in Figure~\ref{fig:spectrum}.

%%%

Table \ref{tab:results} reports the source distances $d_r$ in kpc at which the median of the coverage is lower than 95\% of the noise only values for aLIGO, AdV, and different configurations of third-generation detectors. We have checked that using either the median of the coverage or the median of $\Delta$ yield similar results for the distance.
The numbers on the table are an estimate of the order of magnitude of the source maximal distance at which a
reconstruction of the ratio could be possible with current and planned GW detectors.
They are also upper limits as we are taking into account the detector antenna response in our
simulation but assume that the source is optimally oriented with a matched filter signal-to-noise ratio of 13. 
Table \ref{tab:results} shows that the results for the Advanced Virgo detector at design sensitivity are very similar to those of aLIGO, despite the differences in detector sensitivity.
%Note that Table \ref{tab:results} provides the distance at which one could detect a source
%optimally oriented with a matched filter signal-to-noise ratio of 13.

Figure \ref{fig:s20--SFHo_all3G} shows $\Delta$ as function of the source distance for {\texttt s20S}
waveform for the five third-generation detector configurations we analyze. Overall, the ratio is well reconstructed up to distances
in the range \unit[100--200]{kpc} which represents an improvement of a factor 10 with respect to
Advanced LIGO and Advanced Virgo detectors. We can also note that the Einstein Telescope results lay in
between the 2 Cosmic Explorer results. This is confirmed for all other waveforms, expect {\texttt s25}
for which the maximal distance reach in CE2 is significantly lower than CE1. This is partly due to the
small variation of the reconstruction quality to the distance of the source making the estimation of $d_r$
rather uncertain for this waveform. All results are summarized in Table \ref{tab:results} and Figure
\ref{fig:distances}. It is remarkable that with 3G detectors the ratio could be reconstructed for sources
located up to several hundred of kpc. It is nevertheless important to note the rather wide range obtained
for the different waveforms probing a large range of progenitor masses.
We did not find any correlation between the mass of the progenitor and $d_r$, nor the equation of state.
On the other hand, the quality
of the ratio reconstruction depends on the signal-to-noise ratio, expressed in Table \ref{tab:results} by
$d_{det}$.
